\LARGE \bf Efficient Sampling for Grasp Quality Evaluation with Gaussian Process Implicit Surface Representation

### 2014-09-17 paper.tex
added sampling and adaptive sampling

\usepackage{amsmath,amssymb}
\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

@@

\title{\LARGE \bf
Grasp Distributions and a Metric for Shape Uncertainty with Gaussian Process Implicit Surface Representation (Draft: Not Finished Work) }

\author{Michael Laskey*, Zoe McCarthy*, Florian T. Pokorny, Jeff Mahler, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space

@@

\vspace{10pt}
Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}. As shown in Fig. \ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.  A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.   However, only recently have people started looking into a metric's robustness to uncertainty.

We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
We are working to extend this metric to incorporate shape uncertainty, and to do that we analyze the resulting distributions over grasp parameters induced by the shape uncertainty.

@@

\section{Contributions To Date}
We assume that a robot's $m$ grippers approach the grasped object along straight lines (which we call lines of action), and analyze how this grasping model interacts with the probability distribution on shapes described by a Gaussian Process Implicit Surface (GPIS).
We calculate and visualize the theoretical probability distributions on grasp contact points and normals and the expected center of mass induced by the GPIS and line of action.
We empirically validate our calculated distributions by measuring their KL-divergence from the empirical probability distributions obtained by sampling from the GPIS distribution and calculating the contact point along the line of action and the corresponding normal for several example shapes.

We show ongoing work in adapting the Ferari-Canny grasp metric to this setting.
We present an algorithm to compute an upper bound on the expected deviation in grasp quality from the metric evaluated at a single grasp using a recent result that Ferrari-Canny is Lipschitz continuous \cite{pokorny2013classical}.
In order to improve the tightness of these bounds and thus improve our algorithm, we show initial investigations into calculating gradients for Ferrari-Canny in order to find very tight locally Lipschitz bounds.
We present a heuristic algorithm based off of the previous algorithm that normalizes the looser bound and quality of expected values and ranks by the difference between them.

@@

@@

@@

We recall the quantity CDF$(f(x))(0) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ as the cumulative distribution function of $f(x)$ evalutated at 0 and note that it is equal to the probability that $x$ is interior to the surface under the current observations.
We assume that the object has uniform mass density and then CDF$(f(x))(0)$ is the expected mass density at $x$.
Then we can find the expected center of mass as:

@@

\section{Probabilistic Bound on Grasp Metric}
\label{sec:bound}
Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we would like to prove an extension to give a probabilistic bound on the change in grasp quality.

With a distribution on $p(g)$ we then use recent results on a Lipschitz constant for the Ferrari-Canny Metric \cite{pokorny2013classical} to provide $b$ or an upper bound on the change in grasp quality from the expected deviation in grasp and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = ( \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau )$.

We restate several of their results here:

\subsection{Prior Work: Derivation of Lipschitz Constant }

We follow the notation of \cite{pokorny2013classical} except that the friction coefficient is $\mu$ in that paper and $\tau$ in this paper since we use $\mu$ to refer to mean vectors.  
We re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ is the exact $L^1$ grasp quality.
It is denoted by the following

\begin{align}
  Q(g) &= \mbox{max}(0,q(g)) = -d(0,\mbox{Conv}(\{0\} \cup S(g))\\
-d(0,S) &= min_{||z|| = 1} h_{S(z)}\\
h_{S(z)} &= \mbox{sup}_{s\in S}\langle s,z\rangle\\
\end{align}

We denote the Ferrari-Canny version, which approximates the friction cone by a linearized set of wrenches\cite{ferrari1992}, as $Q^-_l(g)$.
The next theorem shows that the linearized wrench set used in Ferrari-Canny calculates a lower bound on $Q(g)$.\\

\begin{theorem}
  \cite{pokorny2013classical}
For any grasp g, we have $0 \leq Q_l^-(g) \leq Q(g)$.
Furthermore, $||Q(g) - Q^-_l(g)|| \rightarrow 0$ as $l \rightarrow \infty$ when $Q_l^-(g)$ is computed using a uniform approximation of the friction cones with $l$ edges. \\
\end{theorem}

The next theorems are used to show that $Q$ is Lipschitz continuous.

\begin{theorem}
\label{lemma35}
  \cite{pokorny2013classical}
For $w \in \mathbb{R}^3$, we have, for $n \in \mathbb{S}^2$ and for friction coefficient $\mu > 0$,

\begin{align}
\mbox{sup}_{x \in C(n)} \langle x,w \rangle = \langle n,w \rangle + \tau||n \times w||
\end{align}

Hence, for $u = (a,b) \in \mathbb{R}^3 \times \mathbb{R}^3 = \mathbb{R}^6$, we have

\[
h_{W_i(g)}(a,b) =
 \langle n_i,a+b\times(c_i-z)\rangle +
\]
\begin{align}
 +\tau ||n_i \times (a+b\times(c_i-z))||
\end{align}

\end{theorem}

\begin{theorem}
  \cite{pokorny2013classical}
We have \\

\begin{align}
q(g) 
=
\min_{u\in \mathbb{R}^6, ||u|| =1} h_{S(g)}(u) 
=
\end{align}
\[
\min_{u\in \mathbb{R}^6, ||u|| =1} \max_{i=1,...,m} h_{W_i(g)}(u),
\]

where $h_{S(g)}$ is convex on $\mathbb{R}^6$.
$q$ is invariant under fixed translation of the grasp center and contact positions.
Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$.
Then $q$ is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1, \dots, c_m,n_1, \dots,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where we use distance measure

\[
  d(g,g') = \sum_i ||(c_i-z)-(c_i'-z')|| + \sum_i ||n_i - n_i'||.
\]

We hence have

\[
|q(g) - q(g')| \leq Ld(g,g'),\  \forall g,g' \in X.
\]

Since $Q(g) = \max(0,q(g))$, $Q$ is also Lipschitz continuous with the same constant $L$ on $X$. 
\end{theorem}

Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|\langle n_i,a+b\times (c_i-z)\rangle - \langle n_i',a+b\times(c_i'-z')\rangle|+\mu|||n_i \times (a+b \times (c_i -z))|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}.
By using the following facts $||a|| \leq 1$, $||b|| \leq 1$, $||v \times w || \leq ||w||||v||$, $|\langle v,w\rangle | \leq ||v||||w||$, we obtain:

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||(c_i - z)-(c_i'-z')|| \\
					&+ \tau(||n_i - n_i'||(1+||c_i - z||)\\
					&+||(c_i - z)-(c_i'-z')||)
\end{align*}

\subsection{Upper Bound on Expected Deviation of Grasp Quality}
Given a the distributions on a line of action, $p\big(\textbf{n}_i = \textbf{v}\big)$ and $p\big(\textbf{c}_i=\gamma(t) \big)$ and the expected values $\bar{\textbf{c}_i}$ and $\bar{\textbf{n}_i}$. We are interested in finding the expected deviations for the two parameters, $||\Delta n_i||$ and  $||\Delta c_i||$. Using these expected deviations we then derive an upper bound $b$ for the expected deviation from the quality of the expected grasp.

\[
  ||\Delta n_i|| =  \int_{\mathbb{S}^1} ||\textbf{v} - \bar{\textbf{n}_i}|| p(\textbf{n}_i = \textbf{v}) d\textbf{v}
\]

\[
  ||\Delta c_i|| =  \int_{\mathbb{R}} ||\gamma(t) - \bar{\textbf{c}_i}|| p(\textbf{c}_i = \textbf{v}) dt
\]

We now write the above bound as follows for a given line of action $i$:

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq (1+\tau)||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| \\
  \end{align*}

Here $\bar{\textbf{r}}_i = \bar{\textbf{c}}_i - \bar{\textbf{z}}_i$. For convenience we rewrite the bound on a given set of grasp parameters as :

 \begin{align*}
b_i &= (1+\tau)(||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| )\\
\end{align*}

To provide an upper bound overall contact parameters we introduce the following:

\begin{align}
b  = \max_{i} b_i
\end{align}

To prove if  this bound is preserved on

 \begin{align}
 q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
 \end{align}

we turn to the general case.
$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b$ and $\lambda(x)$ is bounded.
Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.

\subsection{Tightening Bounds on Change in Grasp Quality}

Experimentally we found the Lipschitz bound to be looser than we would like, despite the fact that it is a local bound. We are currently working on tightening the bound by using the following property:

For a $x,x_0$ in a bounded set $U$ in $\mathbb{R}^n$, for a given $f(x):\mathbb{R}^n \rightarrow \mathbb{R}$.

\[
  f(x) = f(x_0) + \langle R(x),x-x_0 \rangle
\]

\[
  R(x) = \int_0^1 \frac{d}{dx}f(x_0+t(x-x_0)) dt
\]

Then let $L = \mbox{sup}_{s \in U} |\frac{df(x)}{dx} |$, so $|R(x)| \leq L$ and

\[
  |f(x)-f(x_0)| = |\langle R(x),x-x_0 \rangle| \leq L |x-x_0|
\]

Since we are currently working in 2D, there is no need to approximate the friction cone and the Ferrari-Canny is equal to the true grasp quality. What that means is that one could look at the analytical derivative of the closest facet and use that to bound the metric. Looking at a single facet on the convex hull computed during Ferrari-Canny, one simply computes the derivative of the function $h(g)$, where $h$ returns the absolute distance to the origin $d$ from the facet described by
the input parameters. If a single facet is the closest facet to the origin, then the gradient of the Ferrari-Canny metric at that point is the gradient of the distance of that facet to the origin, calculated using the chain rule.

While we can compute the derivative using the computer algebra system sympy \cite{SymPy}, it is still on going work to quickly determine either the set $U$ that the bound is valid or supremum of the derivative in a given set.

\subsection{Approximation of True Metric}
While we work on the tightening the bound, we will present a metric that should give an intuitive idea of what is import in our grasp metric. Our grasp metric currently returns $Q(\bar{g})$ and an upper bound $b$ on the expected change in grasp quality. Ideally we want to rate grasps by the highest value $Q_l = Q(\bar{g}) - b$, thus being the lowest quality given the bound.

Currently though the two values $Q(\bar{g})$ and $b$ are two different magnitudes, but both are informative. We can heuristically approximate a the effect of a tighter bound by simply projecting both $Q(\bar{g})$ and $b$ to the unit ball, then performing the subtraction. Thus we define the following:

\begin{align*}
Q_h = \frac{Q(\bar{g})}{||Q(\bar{g})||} - \frac{b}{||b||}
\end{align*}

@@

To validate our theoretical caculations, we compared them to empirical distributions found via Monte-Carlo Sampling. The qualitative results for surface normals and contacts can be found in Figures \ref{fig:Contact_Dist} and \ref{fig:Normal_Dist} respectively. We present the numerical comparison with KL-divergence in Table 1, as you can see the distributions are very closely related.

@@

To better understand the quality of grasp that our proposed metric will find, we present results on a variety of grasps as shown in Fig. \ref{fig:Grasps}. The numerical values in terms are presented in Table 2.

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide09.jpg} \includegraphics[scale = 0.3]{figures/Slide10.jpg}
\caption{Example grasps on the provided dataset with the histograms of grasp quality given the uncertainity}
\vspace*{-10pt}
\label{fig:Grasps}
\end{figure}

\begin{table}[ht!]
        \begin{tabular}{ l | c c c c}
         Distribution & \bf Marker & \bf Tape & \bf Loofa & \bf Stapler \\ 
        \hline \\
        $E[Q(p(g))]$ & -0.003 & 0.022 & 0.000 &  0.018\\
        \hline \\
        var $Q(g)$ & 0.025 & 0.016 & 0.017 &  0.054\\
        \hline 
        $Q(\bar{g})$ & 0.030 & 0.024 & -0.012 & 0.014\\
        \hline 
        $b$ & 1.634 & 0.540 & 2.220 & 2.600 \\
        \hline 
        $Q_h$ & -0.031 & 0.451 & -0.530 & -0.640 \\
        \hline 
        \end{tabular}
        \caption{A comparison of all the different values that characterize a grasp.}

\vspace*{-20pt}
\end{table}

\bibliographystyle{ieeetr}
\bibliography{references}

>>>>

\usepackage{amsmath,amssymb}

\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{benktools}

\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

@@

\title{\LARGE \bf
Efficient Sampling for Grasp Quality Evaluation with Gaussian Process Implicit Surface Representation }

\author{Michael Laskey, Zoe McCarthy, Florian T. Pokorny, Jeff Mahler, Sachin Patil,\\ Danica Kragic, Jur Van Den Berg, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space

@@

\vspace{10pt}

\todo{Write a better Intro, needs to have a better sell}
Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}. As shown in Fig. \ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.  A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.   However, only recently have people started looking into a metric's robustness to uncertainty.

We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape. Gaussian Processes provide a formal way to incorporate uncertainty, however this sophisticated representation presents new challenges for evaluating the expected grasp quality. The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.

We assume that a robot's $m$ grippers approach the grasped object along straight lines (which we call lines of action), and analyze how this grasping model interacts with the probability distribution on shapes described by a Gaussian Process Implicit Surface (GPIS).
We calculate and visualize the theoretical probability distributions on grasp contact points and normals and the expected center of mass induced by the GPIS and line of action.
Then demonstrate how sampling from this explicit grasp distribution can be used to reduce the complexity associated with Monte-Carlo integration of the expected grasp quality over the distribution of shapes.

We also treat the problem of finding the best grasp in a set of proposed grasps as a n-arm bandit problem and propose an $\epsilon$ - greedy policy for finding the best grasp in the set in an anytime like manner.

@@

\todo{Get an actual Kinect Image}

@@

\todo{Write about n-arm bandit literature}

@@

\todo{Get a better figure for line of action model}

@@

We recall the quantity CDF$(f(x))(0) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ as the cumulative distribution function of $f(x)$ evaluated at 0 and note that it is equal to the probability that $x$ is interior to the surface under the current observations.
We assume that the object has uniform mass density and then CDF$(f(x))(0)$ is the expected mass density at $x$.
Then we can find the expected center of mass as:

@@

\section{Sampling from a GPIS}
Prior work that consider shape uncertainty purposed sampling from distribution on the shape itself \cite{kehoe2012toward}. However, with a more complicated model on the shape distribution this technique would scale poorly.

Given a work space $\mathcal{R}^{n\times n}$, the complexity of sampling a work space is show to be $O(n^6)$. This is due to the necessary inversion of a $n \times n$. In typical cases $n$ would be on the order of 100 making this very computationally intensive even in the 2D case.

If we instead sample from our proposed grasp distributions and use a line of action that is roughly equal to $n$, the complexity can be rewritten as $O(T*n^3)$,  where $T$ is the number of grasps that are evaluated.

\section{Adaptive Sampling for Grasp Selection}
In a possible grasping scenario, one would be presented with a set $G$ of $T$ grasps. The goal would be to identify, which one is the best grasp given the set $G$ and for each grasp the $p(g)$. While a naive approach to solving this problem would be to simply perform Monte-Carlo integration on each one and compute the expected grasp quality, we propose treating the problem as an n-arm bandit problem and forming a policy for selecting which grasp to sample. The motivation behind this is due to the expensive evaluation that each Ferrari-Canny computation takes \cite{ferrari1992}.

An n-arm bandit problem can be defined as follows: an agent is presented with a $n$ slot machines and receives a reward each time a lever is pulled that is drawn from the distribution associated with the slot machine. The goal of the agent is to maximize the expected reward received, by balancing exploration and exploitation \cite{barto1998reinforcement}.

For selecting grasps we use an $\epsilon$-greedy policy, where the greedy action is selected with probability $1-\epsilon$ and a random action is chosen otherwise. The greedy option is defined as the grasp with the highest approximate upper confidence bound $v$, which is computed via the following \cite{mc}

\begin{equation}
v = \bar{X} + \frac{1.96 \bar{\sigma}_N}{\sqrt{n}}
\end{equation}

@@

\subsection{Validation of Grasp Distributions}

To validate our theoretical calculations, we compared them to empirical distributions found via Monte-Carlo Sampling. The qualitative results for surface normals and contacts can be found in Figures \ref{fig:Contact_Dist} and \ref{fig:Normal_Dist} respectively. We present the numerical comparison with KL-divergence in Table 1, as you can see the distributions are very closely related.

@@

\subsection{Sampling from Grasps Vs. Shape}
We first demonstrate that sampling from the two different method converges to near the same expected value, see Fig. \ref{fig:sampling_convergence}. After confirming the distributions converge to the same value we show the computational complexity in Fig. \ref{fig:speed_dif} of the two methods for evaluating 100 grasps on an $n \times n$ grid.

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide11.jpg}
\caption{Left: Sampling from grasp distributions
Right: Sampling from distribution on shape}
\vspace*{-10pt}
\label{fig:sampling_convergence}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide12.jpg}
\caption{Comparison of the computational complexity of the two methods with respect to the work space dimensions}
\vspace*{-10pt}
\label{fig:speed_dif}
\end{figure}

\subsection{Adaptive Sampling Technique}

We consider the problem of selecting the best grasp out of a set $G$ given a fix number of iterations $I$. For our experiments we look at selecting the best grasp out of a size of $|G| = 100$ and given a fix iteration limit of $I = 1000$. We show the results for both the marker and tape, in Fig. \ref{fig:marker_bandit} and Fig. \ref{fig:tape_bandit} respectively. We note that in both cases the policy was able to select the best grasp without sufficiently sample the set of possible grasps.

\todo{Add experiments demonstrating ordering and trials over large number of runs, also fix visualizations}

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide09.jpg}
\caption{Left: $\epsilon$-greedy policy for sampling (Top 10 grasps plotted)
Right: Monte-Carlo Sampling for 1000 iterations (Top 10 grasps plotted)}
\vspace*{-10pt}
\label{fig:marker_bandit}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide10.jpg}
\caption{Left: $\epsilon$-greedy policy for sampling (Top 10 grasps plotted)
Right: Monte-Carlo Sampling for 1000 iterations (Top 10 grasps plotted)}
\vspace*{-10pt}
\label{fig:tape_bandit}
\end{figure}

\todo{Write Conclusion}
\bibliographystyle{ieeetr}
\bibliography{references}
